\sysfull

### 2017-11-17 paper/intro.tex
revisions abs and intro

\textbf{Task Coalescing.} To address this challenge we propose a \emph{dynamic} task decomposition, that accepts any static decomposition and opportunistically coalesces tasks at runtime when there is sufficient energy. With \emph{task coalescing} atomic tasks are merged into a single (larger) task while preserving atomicity of the merged task. If power fails while a coalesced task is running, execution will restart at the first task in the group. Figure~\ref{fig:coalescing} (bottom) illustrates how dynamic coalescing changes the earlier execution and highlights the change in memory model necessary to not break atomicity.

@@

We evaluated \sys end-to-end on a real energy-harvesting device~\cite{wisp} running existing benchmarks ~\cite{chain} and new programs. A comparison to a state-of-the-art task-based system~\cite{chain} showed that \sys recovers
performance on conservative task decompositions missed by systems with static decomposition.
%
%and can flexibly target a variety of platforms without rewriting code.
%
\todo{Provide concrete numeric results supporting this claim}{Amjad/Przemek}

>>>>

\textbf{Task Coalescing.} To address this challenge we propose a \emph{dynamic} task decomposition, that accepts any static decomposition and opportunistically coalesces tasks at runtime when there is sufficient energy. With \emph{task coalescing} atomic tasks are merged into a single (larger) task while preserving atomicity of the merged task. If power fails while a coalesced task is running, execution will restart at the first task in the group. Figure~\ref{fig:coalesce} (bottom) illustrates how dynamic coalescing changes the earlier execution and highlights the change in memory model necessary to not break atomicity.

@@

We evaluated \sys end-to-end on a real energy-harvesting device~\cite{wisp} running existing benchmarks ~\cite{chain} and new programs. A comparison to a state-of-the-art task-based system~\cite{chain} showed that \sys recovers
performance on conservative task decompositions missed by systems with static decomposition.
%
%and can flexibly target a variety of platforms without rewriting code.
%
%\todo{Provide concrete numeric results supporting this claim}{Amjad/Przemek}
